%%Chapter - Split into separate file if too large
\chapter{Breakfast/Brunch}
%%Start recipe
\newrecipe{Boston Style Baked Beans with Ham}{}
\section*{Ingredients}
\begin{ingredients-list}
	\item 400g dried cannellini beans
	\item 2 tsp vegetable oil
	\item 1 large onion finely diced
	\item 1.5 kg ham hock
	\item 1 bay leaf
	\item 60 ml molasses
	\item 80 g brown sugar
	\item 160 g tomato paste
	\item 2 tbsp Worcestershire sauce
	\item 1 tsp mustard powder
	\item 1 garlic clove 
\end{ingredients-list}

\section*{Directions}
\begin{enumerate}
	\item Soak the beans in a large saucepan of water overnight. Drain well, rinse and drain again.
	\item Heat the oil in a large saucepan and brown the onion for 5 minutes or until golden. Add the beans, ham hock, bay leaf and 3 litres of water and bring to the boil.
		Reduce the heat and simmer for 1 hour, stirring occasionally.  Drain Reserving the liquid.
	\item Combine 3 cups of the reserved bean liquid with the molasses, brown sugar, mustard, Worcestershire sauce, tomato paste and garlic and pour into saucepan.
		Add enough of the remaining cooking liquid to cover the beans. Cover and cook over low heat for 3 hours, stirring occasionally and turning the ham hock halfway through.
	\item Remove the ham hock and cut the meat from the bone. Cut the meat into smallish chunks then return the dish and stir to combine.
		Cook uncovered for 30 minutes, or until the sauce is thick and syrupy.
	\item Serve with thick toast and poached eggs.
\end{enumerate}
**REF: Grimes, L. (2010). Vegetables. In \textit{Cook's book of everything} (p. 406). Sydney: Murdoch Books.


%%End recipe

%%Start Recipe
\newrecipe{Buttermilk Pancakes}{}

\section*{Ingredients}
\begin{ingredients-list}
	\item \sfrac{1}{4} cup caster sugar
	\item \sfrac{1}{4} teaspoon bicarbonate of soda
	\item 1 cup self-raising flour, sifted
	\item 1\sfrac{1}{4}   cups buttermilk
	\item 1egg
\end{ingredients-list}

\section*{Directions}
\begin{enumerate}	
	\item Combine dry ingredients in a bowl and whisk together.
	\item Whisk egg and buttermilk in a separate bowl.
	\item Mix the egg/buttermilk mixture into the dry ingredients being careful not to over beat.
	\item Heat fry pan and fry in a little butter. (Use a little under \sfrac{1}{4} cup of batter per pancake)
\end{enumerate}
%%end Recipe