%%Chapter - Split into separate file if too large
\chapter{Vegetarian Main Dishes}
%%Start recipe
\newrecipe{Sweet Potato and Spinach Pasta Rotolo}{http://www.jamieoliver.com/recipes/vegetables-recipes/squash-spinach-pasta-rotolo}
\section*{Ingredients}
\begin{ingredients-list}
	\item 1 butternut squash (roughly 1.2kg) (Substitute Sweet Potato)
	\item 1 red onion
	\item olive oil
	\item 1 teaspoon dried thyme
	\item 500 g frozen spinach
	\item 1 whole nutmeg, for grating
	\item 4 cloves of garlic
	\item 1 x 700 ml jar of passata
	\item 6 large fresh free-range pasta sheets (roughly 15cm x 20cm each)
	\item 50 g feta cheese
	\item20 g Parmesan cheese
\end{ingredients-list}

\section*{Directions}
\begin{enumerate}
	\item Preheat the oven to 180ºC/350ºF/gas 4. Cook the squash whole on a roasting tray for around 1 hour 30 minutes, then remove from the oven. Meanwhile, peel and roughly chop the onion, put it into a medium pan on a medium-low heat with a lug of oil, the thyme and a pinch of salt and pepper, and cook for 10 minutes, stirring occasionally. Stir in the frozen spinach, cover with a lid and allow to slowly cook for another 15 minutes, or until the liquid has evaporated, then remove from the heat. Cut the squash in half, discard the seeds and skin, then mash up with a fork. Keeping them separate, season both the squash and spinach to perfection with salt, pepper and a grating of nutmeg.  If substituting sweet potato rub the sweet potato all over with oil and place on a baking tray in the oven.  Bake for around 45 minutes to 1 hour depending on the size of the sweet potato. Skewer with a toothpick to check them but the skins should be loosened and slightly blackened when cooked.
	\item Peel and finely slice the garlic, then put it into a shallow 28cm casserole pan on a medium heat with a splash of oil and fry for a couple of minutes, or until lightly golden. Pour in the passata, then add a splash of water to the empty jar, swirl it around and pour it into the pan. Bring to the boil, simmer for just 3 minutes, then season to perfection.
	\item On a clean work surface, lay out the pasta sheets facing lengthways away from you. Working quickly so your pasta doesn't dry out, brush them with water, then evenly divide and spread the squash over the sheets. Sprinkle over the cooked spinach and crumble over the feta. Roll up the sheets and cut each one into 4 chunks, then place side by side in the tomato sauce. Finely grate over the Parmesan, then pick the sage leaves (if using), toss in a little oil and scatter over the top. Bake for 35 to 40 minutes at the bottom of the oven until golden and crisp. Delicious served with a fresh green salad.
\end{enumerate}

%%End recipe

%%End Chapter